\addcontentsline{toc}{section}{References}

\begin{thebibliography}{99}

\mywebref{Biology}{Biotech}{http://biotech.icmb.utexas.edu/pages/bioinfo.html}
\mywebref{Bioinformatic}{Information about Bioinformatics}{http://www.absoluteastronomy.com/topics/Bioinformatics}
\mywebref{GO_website}{Gene Ontology}{http://www.geneontology.org/}
\mywebref{OBO}{The Open Biomedical Ontologies}{http://www.obofoundry.org/}

\bibitem{data_clustering_book}
G. Gan, C. Ma and J. Wu, Data Clustering. Theory, Algorithms, and Applications, Society for Industrial and Applied Mathematics pp 3, 2007.

\mywebref{Kerren}{Prof. Dr. Andreas Kerren home page}{http://w3.msi.vxu.se/users/akemsi/}
\mywebref{Schreiber}{Prof. Dr. Falk Schreiber home page}{http://bic-gh.ipk-gatersleben.de/~schreibe/}
\mywebref{ISOVIS}{ISOVIS research group home page}{http://cs.lnu.se/isovis/}
\mywebref{PBG}{Plant Bioinformatic research Group home page}{http://nwg.bic-gh.de/}
\mywebref{Graphlet}{Graphlet}{http://www.fmi.uni-passau.de/Graphlet/}
\mywebref{GML}{GML}{http://www.infosun.fim.uni-passau.de/Graphlet/GML/gml-tr.html}
\mywebref{GML_wiki}{GML supported programs}{http://en.wikipedia.org/wiki/Graph_Modelling_Language}
\mywebref{yEd}{yEd}{http://www.yworks.com/en/products_yed_about.html}
\mywebref{clairlib}{Clairlib}{http://www.clairlib.org/}
\mywebref{Cytoscape}{Cytoscape}{http://en.wikipedia.org/wiki/Cytoscape}
\mywebref{NetworkX}{NetworkX}{http://en.wikipedia.org/wiki/NetworkX}
\mywebref{ocamlgraph}{ocamlgraph}{http://ocamlgraph.lri.fr/}
\mywebref{OGDF}{OGDF}{http://www.ogdf.net/}
\mywebref{Tulip}{Tulip}{http://tulip.labri.fr/TulipDrupal/}
\mywebref{GraphML}{GraphML specification}{http://graphml.graphdrawing.org/}
\mywebref{GXL}{GXL introduction}{http://www.gupro.de/GXL/Introduction/section1.html}
\mywebref{SVG}{SVG information}{http://en.wikipedia.org/wiki/Scalable_Vector_Graphics}
\mywebref{GDC}{Graph Drawing Conference '95}{www.informatik.uni-trier.de/~ley/db/conf/gd/gd95.html}

%\mywebref{Radial_dendrogram}{Radial Dendrogram}{cs.sunysb.edu/~vislab/papers}
%\mywebref{Dendrogram}{Introduction into Dengrograms}{en.wikipedia.org/wiki/Dendrogram}

%\bibitem{Barlow_Neville}
T. Barlow and P. Neville, A comparison of 2D visualization of hierarchies, Information Visualization pp 131-138, 2001.

%\bibitem{Kreussler_Schumann}
M. Kreussler and H. Schumann, A flexible approach for visual data mining, IEEE Trans. VisualGraphics, vol. 8, no. 1, pp. 39-51, 2002.

%\bibitem{Yang_Ward}
J. Yang, M. Ward, and E. Rundensteiner, InterRing: An interactive tool for visually navigating and manipulatiung hierarchical structures, IEEE 2002 Symposium on Information Visualization, pp. 77-92, 2002.

\mywebref{java_com}{Java FAQ}{http://www.java.com/en/download/faq/whatis_java.xml}

\mywebref{BINARY_TREE}{Binary Tree definition}{http://www.wordiq.com/definition/Binary_tree}

\mywebref{JAVA_2D}{Java 2D reference}{http://java.sun.com/products/java-media/2D/reference/index.html}

\mywebref{JAVA_AWT}{Java AWT overview}{http://en.wikipedia.org/wiki/Abstract_Window_Toolkit}

\mywebref{JAVA_SWING}{Java SWING overview}{http://en.wikipedia.org/wiki/Swing_(Java)}

\mywebref{AWT_VS_SWING}{AWT vs SWING comparison}{http://edn.embarcadero.com/article/26970}

\mywebref{MAVEN_HOME_PAGE}{Maven project home page}{http://maven.apache.org/}

\mywebref{APACHE_FOUNDATION_HOME_PAGE}{Apache Foundation home page}{http://www.apache.org/}

\bibitem{MAVEN_BOOK_1}
Vincent Massol, Jason van Zyl, Better builds with Maven, Mergere Library Press, pp. 16, 2006.

\bibitem{MAVEN_BOOK_1}
Vincent Massol, Jason van Zyl, Better builds with Maven, Mergere Library Press, pp. 18, 2006.

\mywebref{REVISION_CONTROL}{Revision Control definition}{http://en.wikipedia.org/wiki/Revision_control}

\mywebref{GIT}{Git overview}{http://en.wikipedia.org/wiki/Git_(software)}

\mywebref{}{}{}

\mywebref{GEF}{Java Graph Editing Framework}{http://gef.tigris.org/}

\mywebref{ILOG_Jview}{ILOG Jview}{http://www.ilog.com/products/jviews/}

\mywebref{JGraphT}{JGraphT)}{http://jgrapht.sourceforge.net/}

\mywebref{JUNG}{Java Universal Network / Graph Framework (JUNG)}{http://jung.sourceforge.net/}

\mywebref{JUNG_OVERVIEW}{JUNG graph library overview}{http://jung.sourceforge.net/index.html}

\mywebref{EXTC}{ExtC}{http://code.google.com/p/ext-c/}

\mywebref{DJINN}{Djinn}{http://www.jnovation.net/djinn}

\mywebref{ANGUR}{Angur}{http://angur.sourceforge.net/}

\mywebref{RDF_GRAVITY}{RDF Gravity}{http://semweb.salzburgresearch.at/apps/rdf-gravity/index.html}

\mywebref{GUESS}{GUESS}{http://www.hpl.hp.com/research/idl/projects/graphs/index.html}

\mywebref{ADAPTNET}{ADAPTNet}{http://bioinformatics.picr.man.ac.uk/adaptnet}

\mywebref{AUGUR}{Augur}{http://www.cs.washington.edu/homes/jfroehli/publications/GROUP2005_SeekingTheSource.pdf}

\mywebref{AUGUR_2}{Jon Froehlich web page}{http://www.cs.washington.edu/homes/jfroehli/}

\mywebref{ARIADNE}{Ariadne}{http://projects.ischool.washington.edu/mcdonald/cscw04/papers/desousa-cscw04.pdf}

\mywebref{NETSIGHT}{Netsight}{http://jung.sourceforge.net/netsight}

\mywebref{INFOVIS_CYBERINFRASTRUCTURE} {InfoVis CuberInfrastructure}{http://iv.slis.indiana.edu/sw/}

\mywebref{PWCOMP}{PWComp}{http://www.ocf.berkeley.edu/\~Ejadelman/pwcomp/}

\mywebref{GOOGLE_CARTOGRAPHY}{Google Cartography}{http://richard.jones.name/google-hacks/google-cartography/google-cartography.html}

\mywebref{GINY}{GINY}{http://csbi.sourceforge.net/}

\mywebref{GRAPHEXPLORER}{GraphExplorer}{http://graphexplore.cgt.duke.edu/}

\mywebref{TOTEM}{TOTEM}{http://totem.run.montefiore.ulg.ac.be/}

\mywebref{D2K}{D2K}{http://alg.ncsa.uiuc.edu/do/downloads}

\mywebref{GRAPHBUILDER}{graphBuilder}{http://aadc-maps.aad.gov.au/analysis/gb.cfm}

\mywebref{SEMIOPHORE}{Semiophore}{http://www.semiophore.net/}

\mywebref{XHOLON}{Xholon}{http://sourceforge.net/projects/xholon/}

\mywebref{FLINK}{Flink}{http://flink.semanticweb.org/}

\mywebref{SWC}{Semantic Web Challenge}{http://challenge.semanticweb.org/}

\mywebref{T_PROX}{T-Prox}{http://www.t-prox.net/}

\mywebref{SIMPLE_C_K_EDITOR}{Simple C-K Editor}{http://code.google.com/p/ckeditor}

\mywebref{PCOPGENE}{PCOPGene}{http://revolutionresearch.uab.es/}

\bibitem{THE_RED_BOOK}
Dave Shreiner, Mason Woo, Jackie Neider, Tom Davis, OpenGL(R) Programming Guide: The Official Guide to Learning OpenGL(R), Version 2.1 (6th Edition), Addison-Wesley Professional, 2007.

\mywebref{LWJGL}{LWJGL}{http://www.lwjgl.org/}

\mywebref{JOGL}{JOGL}{http://jogamp.org/}

\mywebref{Piccolo}{Piccolo}{http://www.cs.umd.edu/hcil/jazz/}

\mywebref{VTK}{Visualisation Toolkit}{http://www.vtk.org/}

\mywebref{InfoVis_Toolkit}{InfoVis Toolkit)}{http://ivtk.sourceforge.net/}

\mywebref{Improvise}{Improvise project homepage}{http://www.cs.ou.edu/~weaver/improvise/index.html}

\end{thebibliography}